### 2010-02-21 sarahDraft.tex
Put what I missed from the outline in my draft

>>>>

\section{Theoretical Stuff} 
	\subsection{Bayesian Statistics}
	   	Bayes' Theorem \\
    	Useful for hierarchical modeling: look at section 3.3 in book. \\
    	Can use Markov Chain Monte Carlo (MCMC) to calculate posterior 
			distribution- bimodal issues.
	\subsection{BRugs/R}
    	All of our statistical analysis was performed in R.  \\
    	All of our modeling was performed using BRugs, which allowed us to use 
			WinBUGS commands and stuff in R.
